---
title: "Discrete Rolling Reserve Policies"
subtitle: "A self-contained simulation study"
author: |
  Sebastián Calcetero Vanegas  
  Independent Researcher, Toronto, Ontario, Canada
date: "September 2026"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    self_contained: true
    theme: cosmo
    highlight: tango
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: true
    latex_engine: pdflatex
    keep_tex: false
    highlight: tango
fontsize: 10pt
geometry: margin=0.82in
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \setlength{\parskip}{0.35em}
---

<style type="text/css">
body { max-width: 1120px; }
pre { font-size: 0.84em; line-height: 1.32; }
table { font-size: 0.92em; }
.table > thead > tr > th { border-bottom: 2px solid #4f6573; }
.caption { color: #4b5963; }
</style>

```{r setup, include=FALSE}
figure_device <- if (knitr::is_latex_output()) "pdf" else "png"
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  collapse = TRUE,
  fig.align = "center",
  dev = figure_device,
  dpi = 160,
  out.width = "100%"
)
options(width = 92, scipen = 4, digits = 5)
```

# Purpose and design

The paper treats reserve selection as a decision problem layered on a predictive
reserving model. At weekly review $n$, that model supplies the conditional law
$F_n$ of the outstanding liability $L_n$. Given the previously carried reserve
$R_{n-1}$, the insurer selects the new reserve from the rolling objective

\[
R_n^*
=\underset{r>0}{\operatorname{arg\,min}}\left\{
c_n^o\,\mathbb E_n[(r-L_n)^+]
+c_n^u\,\mathbb E_n[(L_n-r)^+]
+\Psi_n(r,R_{n-1})
\right\}.
\]

Here, $c_n^o$ and $c_n^u$ are the reduced-form marginal costs of excess reserve
and reserve shortfall, respectively, while $\Psi_n$ assigns a cost to revising
the reserve. The paper studies three choices:

\[
\begin{aligned}
\text{frictionless:}\quad
&\Psi_n(r,R_{n-1})=0,\\
\text{quadratic proportional:}\quad
&\Psi_n(r,R_{n-1})=
\eta_n\left(\frac{r-R_{n-1}}{R_{n-1}}\right)^2,\\
\text{absolute value:}\quad
&\Psi_n(r,R_{n-1})=\eta_n|r-R_{n-1}|.
\end{aligned}
\]

The first choice produces the conditional quantile
$F_n^{-1}\{c_n^u/(c_n^o+c_n^u)\}$. The quadratic policy moves gradually toward
that contemporaneous benchmark, whereas the absolute-value policy leaves the
reserve unchanged inside an endogenous no-action band and moves it to the
nearest boundary otherwise. The code below implements these objectives at each
discrete review date.

This report reproduces the controlled simulation study for the discrete rolling
reserve policies. It is deliberately self-contained: the predictive
distributions, policy functions, robust solvers, performance measures, figures,
and checks are all generated by the code below. No fitted data object or external
simulation output is read.

There are $N=52$ weekly review dates. At review $n$, the liability has a known
Gamma predictive distribution with mean $m_n$ and coefficient of variation
$v_n$:

\[
L_n\mid\mathcal F_{t_n}\sim\operatorname{Gamma}(\alpha_n,\beta_n),
\qquad
\alpha_n=v_n^{-2},\qquad \beta_n=m_nv_n^2,
\]

where $\beta_n$ is the scale parameter. The experiment is not intended to
establish empirical superiority. Its purpose is to make the policy mechanisms
observable under a known law and to measure the adequacy cost of reserve
stability.

We use $c^o=1$ and $c^u=3$. These are reduced-form marginal decision costs,
so the frictionless critical probability is

\[
q=\frac{c^u}{c^o+c^u}=0.75.
\]

The corresponding buffer is therefore generated by the cost asymmetry rather
than imposed as an external VaR constraint.

```{r design-parameters}
# Global experiment settings. Only base R and knitr are required.
N <- 52L
c_over <- 1
c_under <- 3
C_cost <- c_over + c_under
q_star <- c_under / C_cost

# Three revision-cost configurations. "Balanced" is a central reference,
# not an estimated optimum or a universally recommended calibration.
scenario_spec <- data.frame(
  Configuration = c("Reactive", "Balanced", "Stable"),
  QuadraticLambda = c(0.10, 1.50, 5.00),
  EtaAbsolute = c(0.10, 0.42, 0.62),
  stringsAsFactors = FALSE
)

# KL radii are studied separately while balanced revision costs are fixed.
ambiguity_spec <- data.frame(
  Ambiguity = c("Small", "Moderate", "Large"),
  Epsilon = c(0.005, 0.080, 0.250),
  stringsAsFactors = FALSE
)

stopifnot(
  q_star > 0,
  q_star < 1,
  all(q_star - scenario_spec$EtaAbsolute / C_cost > 0),
  all(q_star + scenario_spec$EtaAbsolute / C_cost < 1)
)
```

# Predictive environment

The mean and CV sequences are evaluated only at the 53 displayed grid points
$n=0,\ldots,52$. The four quarters create distinct environments: a relatively
stable opening, an oscillatory transition, a pronounced middle-year reversal,
and a persistent late increase. The policies never interpolate between weekly
reviews.

For transparency, the deterministic functions used to construct this sequence
are stated explicitly. Define

\[
S(x;a,b)=\frac12\left\{1+\tanh\left(\frac{x-a}{b}\right)\right\},
\qquad
w(x)=S(x;0.27,0.035)\{1-S(x;0.66,0.05)\}.
\]

The predictive mean is

\[
\begin{aligned}
m(x)={}&100+8\{1-S(x;0.22,0.07)\}+1.2\sin(14\pi x)\\
&+0.7\cos(24\pi x+0.25)+0.45\sin(34\pi x+0.60)\\
&+w(x)\left[8.5\sin\{8\pi(x-0.25)\}
+3.2\sin\{18\pi(x-0.25)\}\right]\\
&+3.2S(x;0.62,0.045)\{1-S(x;0.78,0.05)\}\\
&+24S(x;0.73,0.05)\frac{x-0.73}{0.27},
\end{aligned}
\]

and its coefficient of variation is

\[
\begin{aligned}
v(x)=\max\Big\{0.045,\;&0.060
+0.100S(x;0.25,0.035)\{1-S(x;0.66,0.05)\}\\
&+0.030S(x;0.72,0.05)
+0.008\sin(10\pi x+0.4)
+0.003\cos(18\pi x)\Big\}.
\end{aligned}
\]

The experiment evaluates $m_n=m(x_n)$ and $v_n=v(x_n)$ at
$x_n=n/N$, so these formulas define the complete Gamma predictive law at every
weekly review.

```{r predictive-environment-functions}
# Smooth transition used to construct the deterministic mean and CV sequences.
S <- function(t, center, width) {
  0.5 * (1 + tanh((t - center) / width))
}

mean_liability <- function(t) {
  early_level <- 8 * (1 - S(t, 0.22, 0.07))
  small_oscillation <-
    1.20 * sin(14 * pi * t) +
    0.70 * cos(24 * pi * t + 0.25) +
    0.45 * sin(34 * pi * t + 0.60)

  middle_window <- S(t, 0.27, 0.035) * (1 - S(t, 0.66, 0.05))
  middle_movement <- middle_window * (
    8.5 * sin(8 * pi * (t - 0.25)) +
    3.2 * sin(18 * pi * (t - 0.25))
  )

  recovery <-
    3.2 * S(t, 0.62, 0.045) * (1 - S(t, 0.78, 0.05))
  late_trend <- S(t, 0.73, 0.05) * 24 * (t - 0.73) / 0.27

  100 + early_level + small_oscillation + middle_movement +
    recovery + late_trend
}

liability_cv <- function(t) {
  middle_window <- S(t, 0.25, 0.035) * (1 - S(t, 0.66, 0.05))
  late_level <- S(t, 0.72, 0.05)
  local_movement <-
    0.008 * sin(10 * pi * t + 0.4) +
    0.003 * cos(18 * pi * t)

  pmax(
    0.060 + 0.100 * middle_window + 0.030 * late_level +
      local_movement,
    0.045
  )
}

make_input <- function(cv_multiplier = 1) {
  week <- 0:N
  time <- week / N
  mean <- mean_liability(time)
  cv <- cv_multiplier * liability_cv(time)
  shape <- 1 / cv^2
  scale <- mean * cv^2

  list(
    week = week,
    time = time,
    decision = 2:length(week),
    mean = mean,
    cv = cv,
    shape = shape,
    scale = scale,
    frictionless = qgamma(q_star, shape = shape, scale = scale),
    cv_multiplier = cv_multiplier
  )
}

input <- make_input()
input$initial <- input$frictionless[1L]
```

The next helpers evaluate the predictive CDF, its inverse, and the exact expected
asymmetric adequacy cost. For a Gamma variable, the truncated first moment is
available through a Gamma CDF with shape increased by one; Monte Carlo is not
needed for the performance calculations.

```{r predictive-distribution-helpers}
cdf_at <- function(reserve, input) {
  pgamma(reserve, shape = input$shape, scale = input$scale)
}

quantile_at <- function(probability, input) {
  qgamma(probability, shape = input$shape, scale = input$scale)
}

expected_adequacy <- function(reserve, input) {
  probability <- cdf_at(reserve, input)
  truncated_mean <- input$mean * pgamma(
    reserve,
    shape = input$shape + 1,
    scale = input$scale
  )

  expected_over <- reserve * probability - truncated_mean
  expected_under <-
    input$mean - truncated_mean - reserve * (1 - probability)

  c_over * expected_over + c_under * expected_under
}

# One smooth, serially correlated Gamma-marginal realization is included only
# as a visual scale reference. It is not used to calculate any policy or metric.
simulate_gamma_path <- function(input, seed = 13782L, rho = 0.98) {
  set.seed(seed)
  latent <- numeric(length(input$week))
  latent[1L] <- rnorm(1L)
  innovations <- rnorm(length(input$week) - 1L)

  for (i in 2:length(latent)) {
    latent[i] <- rho * latent[i - 1L] +
      sqrt(1 - rho^2) * innovations[i - 1L]
  }

  probabilities <- pmin(pmax(pnorm(latent), 1e-10), 1 - 1e-10)
  qgamma(
    probabilities,
    shape = input$shape,
    scale = input$scale
  )
}

simulated_liability <- simulate_gamma_path(input)
```

# Nominal rolling policies

## Frictionless rule

Without revision costs, the reserve at week $n$ is simply

\[
Q_n=F_n^{-1}(q).
\]

This is already stored as `input$frictionless`.

## Quadratic proportional-adjustment rule

For a quadratic penalty, we set

\[
\eta^{(2)}=\lambda(c^o+c^u)R_0.
\]

Given the previous reserve, the new reserve is the scalar root of

\[
(c^o+c^u)F_n(r)-c^u+
2\eta^{(2)}\frac{r-R_{n-1}}{R_{n-1}^2}=0.
\]

Convexity places the root between the previous reserve and the current
frictionless reserve. This gives a stable numerical bracket and makes the code
particularly transparent.

```{r quadratic-policy}
quadratic_policy <- function(lambda, input) {
  eta <- lambda * C_cost * input$initial
  reserve <- numeric(length(input$week))
  reserve[1L] <- input$initial
  residual_at_solution <- numeric(length(input$week))

  for (i in input$decision) {
    previous <- reserve[i - 1L]
    frictionless <- input$frictionless[i]

    # First-order condition at the current week.
    residual <- function(r) {
      C_cost * pgamma(
        r,
        shape = input$shape[i],
        scale = input$scale[i]
      ) - c_under +
        2 * eta * (r - previous) / previous^2
    }

    bracket <- sort(c(previous, frictionless))
    if (diff(bracket) <= 1e-12 * max(1, bracket[2L])) {
      reserve[i] <- frictionless
    } else {
      reserve[i] <- uniroot(
        residual,
        interval = bracket,
        tol = 1e-11
      )$root
    }
    residual_at_solution[i] <- residual(reserve[i])
  }

  list(
    reserve = reserve,
    eta = eta,
    max_foc_error = max(
      abs(residual_at_solution[input$decision])
    )
  )
}
```

## Absolute-value rule

For a penalty $\eta^{(1)}|r-R_{n-1}|$, define

\[
A_n=F_n^{-1}\!\left(q-\frac{\eta^{(1)}}{c^o+c^u}\right),
\qquad
B_n=F_n^{-1}\!\left(q+\frac{\eta^{(1)}}{c^o+c^u}\right).
\]

The previous reserve is kept when it lies inside $[A_n,B_n]$; otherwise it is
projected to the nearest boundary. The band is symmetric in probability space,
but it need not be symmetric in reserve units.

```{r absolute-policy}
absolute_policy <- function(eta, input) {
  lower_probability <- q_star - eta / C_cost
  upper_probability <- q_star + eta / C_cost
  lower <- quantile_at(lower_probability, input)
  upper <- quantile_at(upper_probability, input)

  reserve <- numeric(length(input$week))
  reserve[1L] <- input$initial
  action <- rep("Initial", length(input$week))

  for (i in input$decision) {
    previous <- reserve[i - 1L]

    if (previous < lower[i]) {
      reserve[i] <- lower[i]
      action[i] <- "Increase"
    } else if (previous > upper[i]) {
      reserve[i] <- upper[i]
      action[i] <- "Decrease"
    } else {
      reserve[i] <- previous
      action[i] <- "Keep"
    }
  }

  list(
    reserve = reserve,
    lower = lower,
    upper = upper,
    action = action
  )
}
```

# Performance measures

The predictive mean is the operational point-estimate comparator. The main
measures are:

- **adequacy regret:** adequacy cost relative to the frictionless minimum;
- **adequacy gain:** adequacy-cost reduction relative to booking the mean;
- **attained percentile:** $100F_n(R_n)$, averaged over the 52 decisions;
- **movement reduction:** reduction in total variation relative to the mean path;
- **inaction frequency:** fraction of exact keeps under the absolute-value rule.

Revision penalties are intentionally excluded from adequacy regret. Regret is
the adequacy price of stability, not a comparison of objectives that use
different revision weights.

```{r performance-functions}
total_movement <- function(reserve) {
  sum(abs(diff(reserve)))
}

evaluate_path <- function(
    reserve,
    input,
    configuration,
    policy,
    action = NULL) {

  d <- input$decision
  mean_path <- input$mean
  mean_path[1L] <- input$initial

  adequacy_cost <- sum(expected_adequacy(reserve, input)[d])
  optimum_cost <- sum(
    expected_adequacy(input$frictionless, input)[d]
  )
  mean_cost <- sum(expected_adequacy(mean_path, input)[d])
  attained_percentile <- cdf_at(reserve, input)[d]

  movement <- total_movement(reserve)
  mean_movement <- total_movement(mean_path)

  data.frame(
    Configuration = configuration,
    Policy = policy,
    RegretPct = 100 * (adequacy_cost / optimum_cost - 1),
    GainVsMeanPct = 100 * (1 - adequacy_cost / mean_cost),
    AveragePercentile = 100 * mean(attained_percentile),
    ProbabilityDisplacement =
      100 * mean(abs(attained_percentile - q_star)),
    BufferVsMeanPct =
      100 * mean((reserve[d] - mean_path[d]) / mean_path[d]),
    TotalMovement = movement,
    MovementReductionVsMeanPct =
      100 * (1 - movement / mean_movement),
    InactionPct = if (is.null(action)) {
      NA_real_
    } else {
      100 * mean(action[d] == "Keep")
    },
    stringsAsFactors = FALSE
  )
}
```

The following block runs the three configurations and retains both paths and
diagnostics.

```{r run-nominal}
nominal_paths <- list()
nominal_metrics <- list()
nominal_diagnostics <- list()

mean_path <- input$mean
mean_path[1L] <- input$initial
nominal_metrics[[1L]] <- evaluate_path(
  mean_path,
  input,
  "Benchmark",
  "Predictive mean"
)
nominal_metrics[[2L]] <- evaluate_path(
  input$frictionless,
  input,
  "Benchmark",
  "Frictionless reserve"
)

for (j in seq_len(nrow(scenario_spec))) {
  specification <- scenario_spec[j, ]
  quadratic <- quadratic_policy(
    specification$QuadraticLambda,
    input
  )
  absolute <- absolute_policy(
    specification$EtaAbsolute,
    input
  )

  nominal_paths[[specification$Configuration]] <- data.frame(
    Week = input$week,
    Mean = input$mean,
    Simulated = simulated_liability,
    Frictionless = input$frictionless,
    Quadratic = quadratic$reserve,
    Absolute = absolute$reserve,
    BandLower = absolute$lower,
    BandUpper = absolute$upper,
    AbsoluteAction = absolute$action,
    stringsAsFactors = FALSE
  )

  nominal_metrics[[length(nominal_metrics) + 1L]] <- evaluate_path(
    quadratic$reserve,
    input,
    specification$Configuration,
    "Quadratic penalty"
  )
  nominal_metrics[[length(nominal_metrics) + 1L]] <- evaluate_path(
    absolute$reserve,
    input,
    specification$Configuration,
    "Absolute-value penalty",
    action = absolute$action
  )

  nominal_diagnostics[[j]] <- data.frame(
    Configuration = specification$Configuration,
    MaxQuadraticFOCError = quadratic$max_foc_error,
    stringsAsFactors = FALSE
  )
}

nominal_metrics <- do.call(rbind, nominal_metrics)
nominal_diagnostics <- do.call(rbind, nominal_diagnostics)
rownames(nominal_metrics) <- NULL
```

```{r nominal-design-table, echo=FALSE, results='asis'}
design_table <- transform(
  scenario_spec,
  LowerBand = q_star - EtaAbsolute / C_cost,
  UpperBand = q_star + EtaAbsolute / C_cost
)
design_table$ProbabilityBand <- sprintf(
  "[%.4f, %.4f]",
  design_table$LowerBand,
  design_table$UpperBand
)
design_table <- design_table[c(
  "Configuration",
  "QuadraticLambda",
  "EtaAbsolute",
  "ProbabilityBand"
)]
names(design_table) <- c(
  "Configuration",
  "Quadratic lambda",
  "Absolute eta",
  "No-action probability band"
)
knitr::kable(
  design_table,
  digits = c(NA, 2, 2, NA),
  booktabs = TRUE,
  caption = "Revision-cost configurations."
)
```

```{r nominal-results-table, echo=FALSE, results='asis'}
nominal_display <- nominal_metrics[c(
  "Configuration",
  "Policy",
  "RegretPct",
  "GainVsMeanPct",
  "AveragePercentile",
  "MovementReductionVsMeanPct",
  "InactionPct"
)]
names(nominal_display) <- c(
  "Configuration",
  "Policy",
  "Regret (%)",
  "Gain vs mean (%)",
  "Avg. percentile",
  "Movement reduction (%)",
  "Inaction (%)"
)
knitr::kable(
  nominal_display,
  digits = c(NA, NA, 2, 2, 2, 2, 2),
  booktabs = TRUE,
  caption = "Exact known-law performance of the nominal policies."
)
```

The predictive mean occupies an average percentile of
`r sprintf("%.2f", nominal_metrics$AveragePercentile[1])`%, whereas the
frictionless reserve attains 75% by construction. Relative to booking the mean,
the balanced quadratic rule reduces movement by
`r sprintf("%.2f", subset(nominal_metrics, Configuration == "Balanced" & Policy == "Quadratic penalty")$MovementReductionVsMeanPct)`%
at only
`r sprintf("%.2f", subset(nominal_metrics, Configuration == "Balanced" & Policy == "Quadratic penalty")$RegretPct)`%
adequacy regret. The balanced absolute-value rule reduces movement by
`r sprintf("%.2f", subset(nominal_metrics, Configuration == "Balanced" & Policy == "Absolute-value penalty")$MovementReductionVsMeanPct)`%,
keeps the reserve unchanged in
`r sprintf("%.2f", subset(nominal_metrics, Configuration == "Balanced" & Policy == "Absolute-value penalty")$InactionPct)`%
of weekly decisions, and incurs
`r sprintf("%.2f", subset(nominal_metrics, Configuration == "Balanced" & Policy == "Absolute-value penalty")$RegretPct)`%
regret. The stable specification is visibly different: it suppresses more
movement and pays a larger adequacy cost.

## Nominal reserve paths

```{r nominal-plot-helpers}
plot_colors <- c(
  mean = "#7A7A7A",
  simulated = "#1A1A1A",
  frictionless = "#277DA1",
  quadratic = "#E76F51",
  absolute = "#198754",
  band = "#2A9D8F",
  initial = "#6F42C1"
)

all_nominal_values <- unlist(lapply(
  nominal_paths,
  function(x) unlist(x[c(
    "Mean", "Simulated", "Frictionless", "Quadratic",
    "Absolute", "BandLower", "BandUpper"
  )])
))
nominal_limits <- range(all_nominal_values)
nominal_limits <- nominal_limits + c(-0.05, 0.05) * diff(nominal_limits)

draw_nominal_panel <- function(configuration) {
  x <- nominal_paths[[configuration]]
  plot(
    x$Week,
    x$Frictionless,
    type = "n",
    xlim = c(0, N),
    ylim = nominal_limits,
    xlab = "Weekly review n",
    ylab = "Reserve or liability",
    las = 1
  )
  abline(h = pretty(nominal_limits), col = "#E4E4E4", lwd = 0.7)
  abline(v = c(13, 26, 39), col = "#999999", lty = 3)

  polygon(
    c(x$Week, rev(x$Week)),
    c(x$BandLower, rev(x$BandUpper)),
    col = adjustcolor(plot_colors["band"], alpha.f = 0.14),
    border = NA
  )
  lines(
    x$Week, x$Simulated,
    col = plot_colors["simulated"], lwd = 2.6
  )
  points(
    x$Week, x$Simulated,
    col = plot_colors["simulated"], pch = 16, cex = 0.58
  )
  lines(x$Week, x$Mean, col = plot_colors["mean"], lty = 3, lwd = 1.8)
  points(
    x$Week, x$Mean,
    col = plot_colors["mean"], pch = 1, cex = 0.62
  )
  lines(
    x$Week,
    x$Frictionless,
    col = plot_colors["frictionless"],
    lty = 2,
    lwd = 2.2
  )
  points(
    x$Week, x$Frictionless,
    col = plot_colors["frictionless"], pch = 17, cex = 0.66
  )
  lines(x$Week, x$Quadratic, col = plot_colors["quadratic"], lwd = 2.3)
  points(
    x$Week, x$Quadratic,
    col = plot_colors["quadratic"], pch = 15, cex = 0.62
  )
  lines(x$Week, x$Absolute, col = plot_colors["absolute"], lwd = 2.4)
  points(
    x$Week, x$Absolute,
    col = plot_colors["absolute"], pch = 18, cex = 0.74
  )
  points(
    0, input$initial, pch = 8,
    col = plot_colors["initial"], lwd = 2, cex = 1.05
  )
  keep <- x$AbsoluteAction == "Keep" & x$Week > 0
  if (any(keep)) {
    points(
      x$Week[keep], x$Absolute[keep],
      pch = 21, bg = "white", col = plot_colors["absolute"],
      lwd = 1.8, cex = 0.92
    )
  }
  mtext(configuration, side = 3, line = 0.25, font = 2)
}
```

```{r nominal-paths, echo=FALSE, fig.width=8.5, fig.height=9.2, fig.cap="Nominal rolling policies under reactive, balanced, and stable revision costs. The shaded region is the absolute-value no-action band; white-centered green circles mark exact inaction decisions; dotted vertical lines mark quarter boundaries. The simulated liability is a visual reference only."}
old_par <- par(no.readonly = TRUE)
layout(matrix(1:4, ncol = 1), heights = c(1, 1, 1, 0.12))
par(mar = c(3.2, 4.2, 1.6, 0.8), mgp = c(2.3, 0.7, 0))
for (configuration in scenario_spec$Configuration) {
  draw_nominal_panel(configuration)
}
par(mar = c(0, 0, 0, 0))
plot.new()
legend(
  "center",
  ncol = 3,
  bty = "n",
  cex = 0.78,
  legend = c(
    "Simulated liability", "Conditional mean",
    "Cost-implied frictionless reserve", "Quadratic penalty",
    "Absolute-value penalty", "No-action band"
  ),
  col = c(
    plot_colors[c(
      "simulated", "mean", "frictionless", "quadratic", "absolute"
    )],
    adjustcolor(plot_colors["band"], alpha.f = 0.45)
  ),
  lty = c(1, 3, 2, 1, 1, 1),
  lwd = c(2.6, 1.8, 2.2, 2.3, 2.4, 7),
  pch = c(16, 1, 17, 15, 18, NA)
)
par(old_par)
```

# KL-robust counterparts

Robustness is varied independently of the revision penalties. For a proposed
reserve $r$, the least-favourable density is proportional to

\[
\exp\{\theta a_n(L_n;r)\}\,dP_n,
\qquad
a_n(L_n;r)=c^o(r-L_n)^+ + c^u(L_n-r)^+.
\]

The reserve and the exponential tilt are solved jointly subject to the binding
KL equation. For the quadratic rule, the adverse CDF replaces the nominal CDF
in the marginal first-order condition. For the absolute-value rule, the lower
and upper boundaries are each solved with their own adverse tilt. The resulting
least-favourable distribution is a reserve-dependent piecewise exponential tilt
of the Gamma reference law; it is not itself a single Gamma distribution.

Because Gamma scale is proportional to the mean, the robust calculations can be
performed with $L_n/m_n$, $r/m_n$, and the dimensionless tilt
$\theta m_n$. This improves numerical conditioning without changing the KL
divergence or adverse probabilities.

```{r kl-gamma-components}
logspace_add <- function(x, y) {
  z <- pmax(x, y)
  z + log(exp(x - z) + exp(y - z))
}

# Exact normalizer, adverse CDF, expected loss, and KL divergence for the
# piecewise exponential tilt of a mean-one Gamma reference distribution.
gamma_tilt_components <- function(reserve_ratio, tilt, cv) {
  shape <- 1 / cv^2
  scale <- cv^2
  lower_rate <- 1 + scale * tilt * c_over
  upper_rate <- 1 - scale * tilt * c_under

  if (upper_rate <= 0) {
    stop("The tilt has crossed the Gamma moment boundary.")
  }

  lower_scale <- scale / lower_rate
  upper_scale <- scale / upper_rate
  log_lower_probability <- pgamma(
    reserve_ratio,
    shape = shape,
    scale = lower_scale,
    log.p = TRUE
  )
  log_upper_probability <- pgamma(
    reserve_ratio,
    shape = shape,
    scale = upper_scale,
    lower.tail = FALSE,
    log.p = TRUE
  )

  log_z_lower <-
    tilt * c_over * reserve_ratio -
    shape * log(lower_rate) +
    log_lower_probability
  log_z_upper <-
    -tilt * c_under * reserve_ratio -
    shape * log(upper_rate) +
    log_upper_probability
  log_normalizer <- logspace_add(log_z_lower, log_z_upper)
  adverse_cdf <- exp(log_z_lower - log_normalizer)

  lower_first_ratio <- exp(
    pgamma(
      reserve_ratio,
      shape = shape + 1,
      scale = lower_scale,
      log.p = TRUE
    ) - log_lower_probability
  )
  upper_first_ratio <- exp(
    pgamma(
      reserve_ratio,
      shape = shape + 1,
      scale = upper_scale,
      lower.tail = FALSE,
      log.p = TRUE
    ) - log_upper_probability
  )

  lower_conditional_mean <- lower_first_ratio / lower_rate
  upper_conditional_mean <- upper_first_ratio / upper_rate
  expected_loss_ratio <-
    adverse_cdf * c_over *
      pmax(reserve_ratio - lower_conditional_mean, 0) +
    (1 - adverse_cdf) * c_under *
      pmax(upper_conditional_mean - reserve_ratio, 0)

  list(
    log_normalizer = log_normalizer,
    adverse_cdf = adverse_cdf,
    kl = tilt * expected_loss_ratio - log_normalizer,
    right_tail_scale_ratio = 1 / upper_rate
  )
}
```

The inner solver below finds the tilt that exhausts a given KL radius. The outer
solver then finds the reserve whose adverse CDF equals the required marginal
probability.

```{r robust-frictionless-functions}
solve_tilt_for_kl <- function(reserve_ratio, cv, epsilon) {
  if (epsilon <= 0) {
    return(0)
  }

  tilt_limit <- 1 / (cv^2 * c_under)
  high <- tilt_limit / 256

  while (
    gamma_tilt_components(reserve_ratio, high, cv)$kl < epsilon &&
      high < 0.95 * tilt_limit
  ) {
    high <- min(1.7 * high, 0.95 * tilt_limit)
  }

  if (gamma_tilt_components(reserve_ratio, high, cv)$kl < epsilon) {
    high <- (1 - 1e-10) * tilt_limit
  }

  uniroot(
    function(tilt) {
      gamma_tilt_components(reserve_ratio, tilt, cv)$kl - epsilon
    },
    interval = c(0, high),
    tol = 1e-11
  )$root
}

robust_probability_reserve_ratio <- function(
    cv,
    epsilon,
    target_probability) {

  if (epsilon <= 0) {
    return(qgamma(
      target_probability,
      shape = 1 / cv^2,
      scale = cv^2
    ))
  }

  residual <- function(reserve_ratio) {
    tilt <- solve_tilt_for_kl(reserve_ratio, cv, epsilon)
    gamma_tilt_components(reserve_ratio, tilt, cv)$adverse_cdf -
      target_probability
  }

  bracket <- qgamma(
    c(1e-7, 1 - 1e-9),
    shape = 1 / cv^2,
    scale = cv^2
  )
  uniroot(residual, interval = bracket, tol = 1e-10)$root
}

robust_probability_path <- function(
    input,
    epsilon,
    target_probability) {

  ratio <- mapply(
    robust_probability_reserve_ratio,
    cv = input$cv,
    MoreArgs = list(
      epsilon = epsilon,
      target_probability = target_probability
    )
  )
  tilt <- mapply(
    solve_tilt_for_kl,
    reserve_ratio = ratio,
    cv = input$cv,
    MoreArgs = list(epsilon = epsilon)
  )
  components <- Map(
    gamma_tilt_components,
    reserve_ratio = ratio,
    tilt = tilt,
    cv = input$cv
  )

  list(
    reserve = input$mean * ratio,
    ratio = ratio,
    tilt = tilt,
    adverse_cdf = vapply(
      components,
      function(x) x$adverse_cdf,
      numeric(1)
    ),
    kl = vapply(components, function(x) x$kl, numeric(1)),
    right_tail_scale_ratio = vapply(
      components,
      function(x) x$right_tail_scale_ratio,
      numeric(1)
    )
  )
}
```

The quadratic and absolute-value robust policies reuse the same two equations.
Only their marginal probability conditions differ.

```{r robust-revision-functions}
robust_quadratic_policy <- function(
    lambda,
    input,
    epsilon,
    robust_frictionless) {

  eta <- lambda * C_cost * input$initial
  reserve <- numeric(length(input$week))
  reserve[1L] <- input$initial
  foc_error <- kl_error <- numeric(length(input$week))

  for (i in input$decision) {
    previous <- reserve[i - 1L]
    robust_target <- robust_frictionless$reserve[i]

    residual <- function(r) {
      ratio <- r / input$mean[i]
      tilt <- solve_tilt_for_kl(ratio, input$cv[i], epsilon)
      adverse_cdf <- gamma_tilt_components(
        ratio,
        tilt,
        input$cv[i]
      )$adverse_cdf

      C_cost * adverse_cdf - c_under +
        2 * eta * (r - previous) / previous^2
    }

    bracket <- sort(c(previous, robust_target))
    if (diff(bracket) <= 1e-12 * max(1, bracket[2L])) {
      reserve[i] <- robust_target
    } else {
      reserve[i] <- uniroot(
        residual,
        interval = bracket,
        tol = 1e-10
      )$root
    }

    ratio <- reserve[i] / input$mean[i]
    tilt <- solve_tilt_for_kl(ratio, input$cv[i], epsilon)
    component <- gamma_tilt_components(ratio, tilt, input$cv[i])
    foc_error[i] <- residual(reserve[i])
    kl_error[i] <- component$kl - epsilon
  }

  list(
    reserve = reserve,
    eta = eta,
    max_foc_error = max(abs(foc_error[input$decision])),
    max_kl_error = max(abs(kl_error[input$decision]))
  )
}

robust_absolute_policy <- function(eta, input, epsilon) {
  lower_probability <- q_star - eta / C_cost
  upper_probability <- q_star + eta / C_cost
  lower_solution <- robust_probability_path(
    input,
    epsilon,
    lower_probability
  )
  upper_solution <- robust_probability_path(
    input,
    epsilon,
    upper_probability
  )

  reserve <- numeric(length(input$week))
  reserve[1L] <- input$initial
  action <- rep("Initial", length(input$week))

  for (i in input$decision) {
    previous <- reserve[i - 1L]
    lower <- lower_solution$reserve[i]
    upper <- upper_solution$reserve[i]

    if (previous < lower) {
      reserve[i] <- lower
      action[i] <- "Increase"
    } else if (previous > upper) {
      reserve[i] <- upper
      action[i] <- "Decrease"
    } else {
      reserve[i] <- previous
      action[i] <- "Keep"
    }
  }

  list(
    reserve = reserve,
    lower = lower_solution$reserve,
    upper = upper_solution$reserve,
    action = action,
    lower_solution = lower_solution,
    upper_solution = upper_solution,
    max_kl_error = max(abs(c(
      lower_solution$kl[input$decision] - epsilon,
      upper_solution$kl[input$decision] - epsilon
    ))),
    max_probability_error = max(abs(c(
      lower_solution$adverse_cdf[input$decision] - lower_probability,
      upper_solution$adverse_cdf[input$decision] - upper_probability
    )))
  )
}
```

We now hold the balanced revision parameters fixed and solve all three policies
at each KL radius.

```{r run-robust}
balanced_spec <- subset(
  scenario_spec,
  Configuration == "Balanced"
)
balanced_nominal <- nominal_paths[["Balanced"]]

robust_results <- lapply(
  seq_len(nrow(ambiguity_spec)),
  function(j) {
    epsilon <- ambiguity_spec$Epsilon[j]
    robust_frictionless <- robust_probability_path(
      input,
      epsilon,
      q_star
    )
    robust_frictionless$reserve[1L] <- input$initial

    robust_quadratic <- robust_quadratic_policy(
      balanced_spec$QuadraticLambda,
      input,
      epsilon,
      robust_frictionless
    )
    robust_absolute <- robust_absolute_policy(
      balanced_spec$EtaAbsolute,
      input,
      epsilon
    )

    policies <- list(
      "Frictionless reserve" = list(
        reserve = robust_frictionless$reserve,
        nominal = input$frictionless,
        action = NULL
      ),
      "Quadratic penalty" = list(
        reserve = robust_quadratic$reserve,
        nominal = balanced_nominal$Quadratic,
        action = NULL
      ),
      "Absolute-value penalty" = list(
        reserve = robust_absolute$reserve,
        nominal = balanced_nominal$Absolute,
        action = robust_absolute$action
      )
    )

    metrics <- lapply(names(policies), function(policy_name) {
      object <- policies[[policy_name]]
      row <- evaluate_path(
        object$reserve,
        input,
        ambiguity_spec$Ambiguity[j],
        policy_name,
        action = object$action
      )
      row$Epsilon <- epsilon
      row$UpliftVsNominalPct <- 100 * mean(
        object$reserve[input$decision] /
          object$nominal[input$decision] - 1
      )
      row
    })

    d <- input$decision
    diagnostics <- data.frame(
      Ambiguity = ambiguity_spec$Ambiguity[j],
      Epsilon = epsilon,
      FrictionlessKLError = max(abs(
        robust_frictionless$kl[d] - epsilon
      )),
      FrictionlessProbabilityError = max(abs(
        robust_frictionless$adverse_cdf[d] - q_star
      )),
      QuadraticKLError = robust_quadratic$max_kl_error,
      QuadraticFOCError = robust_quadratic$max_foc_error,
      AbsoluteKLError = robust_absolute$max_kl_error,
      AbsoluteProbabilityError =
        robust_absolute$max_probability_error,
      stringsAsFactors = FALSE
    )

    list(
      frictionless = robust_frictionless,
      quadratic = robust_quadratic,
      absolute = robust_absolute,
      metrics = do.call(rbind, metrics),
      diagnostics = diagnostics
    )
  }
)
names(robust_results) <- ambiguity_spec$Ambiguity

robust_metrics <- do.call(
  rbind,
  lapply(robust_results, function(x) x$metrics)
)
robust_diagnostics <- do.call(
  rbind,
  lapply(robust_results, function(x) x$diagnostics)
)
rownames(robust_metrics) <- NULL
rownames(robust_diagnostics) <- NULL
```

```{r robust-results-table, echo=FALSE, results='asis'}
robust_display <- robust_metrics[c(
  "Configuration",
  "Epsilon",
  "Policy",
  "UpliftVsNominalPct",
  "RegretPct",
  "AveragePercentile",
  "MovementReductionVsMeanPct"
)]
names(robust_display) <- c(
  "Ambiguity",
  "Epsilon",
  "Policy",
  "Uplift (%)",
  "Regret (%)",
  "Avg. percentile",
  "Movement reduction (%)"
)
knitr::kable(
  robust_display,
  digits = c(NA, 3, NA, 2, 2, 2, 2),
  booktabs = TRUE,
  caption = paste(
    "KL-robust policies with balanced revision costs held fixed."
  )
)
```

Increasing $\varepsilon$ raises the reserve level but does not mechanically
alter responsiveness. At the largest radius, mean uplift relative to the
corresponding nominal policies is approximately
`r sprintf("%.1f--%.1f", min(subset(robust_metrics, Epsilon == max(Epsilon))$UpliftVsNominalPct), max(subset(robust_metrics, Epsilon == max(Epsilon))$UpliftVsNominalPct))`%.
The attained nominal percentile rises because the robust law allocates more
weight to costly shortfall outcomes. The quadratic and absolute-value policies
still display gradual adjustment and inaction, respectively.

## Robust reserve paths

```{r robust-plot-helper}
robust_colors <- c(
  Small = "#56B4E9",
  Moderate = "#6F42C1",
  Large = "#B2182B"
)

draw_robust_panel <- function(policy_key, panel_title) {
  nominal_series <- switch(
    policy_key,
    frictionless = input$frictionless,
    quadratic = balanced_nominal$Quadratic,
    absolute = balanced_nominal$Absolute
  )
  robust_series <- lapply(robust_results, function(x) {
    x[[policy_key]]$reserve
  })
  policy_color <- switch(
    policy_key,
    frictionless = plot_colors["frictionless"],
    quadratic = plot_colors["quadratic"],
    absolute = plot_colors["absolute"]
  )
  policy_pch <- switch(
    policy_key,
    frictionless = 17,
    quadratic = 15,
    absolute = 18
  )
  limits <- range(
    input$mean,
    simulated_liability,
    nominal_series,
    unlist(robust_series)
  )
  limits <- limits + c(-0.05, 0.05) * diff(limits)

  plot(
    input$week,
    nominal_series,
    type = "n",
    xlim = c(0, N),
    ylim = limits,
    xlab = "Weekly review n",
    ylab = "Reserve or liability",
    las = 1
  )
  abline(h = pretty(limits), col = "#E4E4E4", lwd = 0.7)
  abline(v = c(13, 26, 39), col = "#999999", lty = 3)
  lines(
    input$week,
    simulated_liability,
    col = plot_colors["simulated"], lwd = 2.6
  )
  points(
    input$week, simulated_liability,
    col = plot_colors["simulated"], pch = 16, cex = 0.58
  )
  lines(input$week, input$mean, col = plot_colors["mean"], lty = 3, lwd = 1.8)
  points(
    input$week, input$mean,
    col = plot_colors["mean"], pch = 1, cex = 0.62
  )
  lines(input$week, nominal_series, col = policy_color, lty = 2, lwd = 2.2)
  points(
    input$week, nominal_series,
    col = policy_color, pch = policy_pch, cex = 0.66
  )
  if (policy_key == "absolute") {
    nominal_keep <- balanced_nominal$AbsoluteAction == "Keep" &
      input$week > 0
    points(
      input$week[nominal_keep], nominal_series[nominal_keep],
      pch = 21, bg = "white", col = plot_colors["absolute"],
      lwd = 1.6, cex = 0.84
    )
  }

  for (ambiguity in names(robust_results)) {
    lines(
      input$week,
      robust_results[[ambiguity]][[policy_key]]$reserve,
      col = robust_colors[ambiguity],
      lwd = 2
    )
    points(
      input$week,
      robust_results[[ambiguity]][[policy_key]]$reserve,
      col = robust_colors[ambiguity], pch = 15, cex = 0.52
    )
    if (policy_key == "absolute") {
      robust_keep <- robust_results[[ambiguity]]$absolute$action == "Keep" &
        input$week > 0
      points(
        input$week[robust_keep],
        robust_results[[ambiguity]]$absolute$reserve[robust_keep],
        pch = 21, bg = "white", col = robust_colors[ambiguity],
        lwd = 1.5, cex = 0.80
      )
    }
  }
  points(
    0, input$initial, pch = 8,
    col = plot_colors["initial"], lwd = 2, cex = 1.05
  )
  mtext(panel_title, side = 3, line = 0.25, font = 2)
}
```

```{r robust-paths, echo=FALSE, fig.width=8.5, fig.height=9.2, fig.cap="KL sensitivity by policy. Balanced revision costs are fixed in every panel; only the ambiguity radius changes. White-centered circles mark exact inaction decisions in the absolute-value panel."}
old_par <- par(no.readonly = TRUE)
layout(matrix(1:4, ncol = 1), heights = c(1, 1, 1, 0.12))
par(mar = c(3.2, 4.2, 1.6, 0.8), mgp = c(2.3, 0.7, 0))
draw_robust_panel("frictionless", "Frictionless reserve")
draw_robust_panel("quadratic", "Quadratic proportional penalty")
draw_robust_panel("absolute", "Absolute-value penalty")
par(mar = c(0, 0, 0, 0))
plot.new()
legend(
  "center",
  ncol = 4,
  bty = "n",
  cex = 0.82,
  legend = c(
    "Nominal frictionless",
    "Nominal quadratic",
    "Nominal absolute value",
    paste0(
      "epsilon = ",
      formatC(ambiguity_spec$Epsilon, format = "f", digits = 3)
    )
  ),
  col = c(
    plot_colors[c("frictionless", "quadratic", "absolute")],
    robust_colors
  ),
  lty = c(2, 2, 2, 1, 1, 1),
  pch = c(17, 15, 18, 15, 15, 15),
  lwd = 2
)
par(old_par)
```

# Predictive-dispersion sensitivity

To test whether the qualitative comparison is an artifact of the chosen CV
sequence, the balanced policies are rerun at $0.75v_n$, $v_n$, and
$1.25v_n$, with the mean sequence unchanged.

```{r cv-sensitivity}
cv_sensitivity <- do.call(
  rbind,
  lapply(c(0.75, 1, 1.25), function(multiplier) {
    local_input <- make_input(multiplier)
    local_input$initial <- local_input$frictionless[1L]
    quadratic <- quadratic_policy(
      balanced_spec$QuadraticLambda,
      local_input
    )
    absolute <- absolute_policy(
      balanced_spec$EtaAbsolute,
      local_input
    )

    quadratic_metrics <- evaluate_path(
      quadratic$reserve,
      local_input,
      "Balanced",
      "Quadratic penalty"
    )
    absolute_metrics <- evaluate_path(
      absolute$reserve,
      local_input,
      "Balanced",
      "Absolute-value penalty",
      action = absolute$action
    )

    data.frame(
      CVMultiplier = multiplier,
      QuadraticRegret = quadratic_metrics$RegretPct,
      AbsoluteRegret = absolute_metrics$RegretPct,
      QuadraticMovementReduction =
        quadratic_metrics$MovementReductionVsMeanPct,
      AbsoluteInaction = absolute_metrics$InactionPct
    )
  })
)
```

```{r cv-sensitivity-table, echo=FALSE, results='asis'}
cv_display <- cv_sensitivity
names(cv_display) <- c(
  "CV multiplier",
  "Quadratic regret (%)",
  "Absolute regret (%)",
  "Quadratic movement reduction (%)",
  "Absolute inaction (%)"
)
knitr::kable(
  cv_display,
  digits = 2,
  booktabs = TRUE,
  caption = "Balanced-policy sensitivity to predictive dispersion."
)
```

The ordering is unchanged. Higher predictive dispersion modestly increases
smoothing and widens the absolute-value no-action region, while adequacy regret
remains close to its baseline value.

# Numerical verification

Every reported policy is checked against the equation that defines it. The
largest residual across the nominal and robust calculations is reported below;
values near machine precision confirm that the figures are not artifacts of
loose numerical tolerances.

```{r diagnostics}
diagnostic_values <- c(
  nominal_diagnostics$MaxQuadraticFOCError,
  unlist(robust_diagnostics[-c(1, 2)])
)

diagnostic_summary <- data.frame(
  Check = c(
    "Largest nominal quadratic FOC residual",
    "Largest robust-system residual"
  ),
  MaximumAbsoluteError = c(
    max(nominal_diagnostics$MaxQuadraticFOCError),
    max(unlist(robust_diagnostics[-c(1, 2)]))
  )
)

stopifnot(
  all(is.finite(diagnostic_values)),
  max(diagnostic_values) < 1e-8,
  all(diff(input$week) == 1),
  length(input$week) == N + 1L,
  all(vapply(nominal_paths, nrow, integer(1)) == N + 1L)
)
```

```{r diagnostics-table, echo=FALSE, results='asis'}
diagnostic_display <- diagnostic_summary
diagnostic_display$MaximumAbsoluteError <- formatC(
  diagnostic_display$MaximumAbsoluteError,
  format = "e",
  digits = 2
)
knitr::kable(
  diagnostic_display,
  booktabs = TRUE,
  caption = "Numerical residual checks."
)
```

# Conclusion

The controlled experiment isolates the decision layer from model estimation.
The frictionless rule converts asymmetric adequacy costs into an economically
motivated reserve buffer. The quadratic penalty exchanges a small amount of
adequacy for gradual adjustment, while the absolute-value penalty creates
literal inaction periods and discrete interventions. Moving from reactive to
stable revision costs strengthens both effects in the expected direction.

The balanced configuration is useful as a middle reference because it remains
responsive to the middle-year reversal and late trend while reducing revision
activity. It is not a universal recommendation: a practitioner should calibrate
the cost asymmetry and revision penalties to its own capital, liquidity,
governance, and implementation environment.

KL robustness answers a different question. It raises the reserve against
predictive model uncertainty while leaving the selected revision-cost regime
fixed. The simulation therefore confirms the intended separation: robustness
changes the predictive measure or reserve level, whereas revision penalties
control how the booked reserve responds from one review to the next.

```{r session-information, echo=FALSE}
cat(
  "Report generated with ",
  R.version.string,
  ".\n",
  sep = ""
)
```
